Automated Verification Applied to Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-07-22 Tex/Old text/chapters/chapter04.tex
thesis updated text

This Chapter is devoted to the results of using automated verification to validate the intended behavior of stand-alone solar PV systems. Moreover, there is the comparative with a specialized simulation tool, and even the use of different verifiers who perform the automated verification in order to evaluate performance.

@@

\begin{table}
\caption{Case studies: stand-alone solar PV systems.}\label{tab2}
\begin{scriptsize}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\hline
Item & House 1 & House 2 & House 3 & House 4 & House 5\\
\hline
\hline
PV Panels &  \multicolumn{4}{|c|}{3x 325 W: in series} & 4x 325 W: 2x series, 2x parallel \\
\hline
Batteries & \multicolumn{4}{|c|}{\makecell{4x220 Ah: 2x series, 2x parallel\\ autonomy: 48 h}} & \makecell{4x 120 Ah batteries in series\\ autonomy: 6 h}\\
\hline
Charge Controller & \multicolumn{5}{|c|}{With MPPT of 150 V/35 A}\\
\hline
Inverter & \multicolumn{4}{|c|}{700 W, peak of 1,600 W} & 1,200 W, peak of 1,600 W\\
\hline
Power demand & 253 W & 263 W & 283 W & 501 W & 915 W\\
\hline
GPS Coordinates & \multicolumn{4}{|c|}{\makecell{2$^{o}$44'50.0"S 60$^{o}$25'47.8"W\\}} & \makecell{3$^{o}$4'20.208"S \\60$^{o}$0'30.168"W}\\
\hline
Details & \multicolumn{4}{|c|}{\makecell{Riverside indigenous community\\Rural Area of Manaus - Brazil}} & \makecell{Urban house \\Manaus-Amazonas-Brazil}\\
\hline
\hline
\end{tabular}
\end{scriptsize}
\end{table}

@@

\section{Verifiers Environment}
\label{sec:verifenviron}

Screens and comments about the verifiers.

\subsubsection{CBMC}

\subsubsection{ESBMC}

\subsubsection{CPAchecker}

\section{HOMER Pro Environment}
\label{sec:homerenviron}

Screens and comments about the simulation tool.

%------------------------------------------
\section{Results and Discussion}
\label{sec:results_indeed}
%------------------------------------------
%
%\textcolor{red}{We should answer the two% research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
%\begin{enumerate}
%\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
%\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
%
Table~\ref{cases} summarizes the results. The times reported in Table~\ref{cases} answer RQ2. 
Note that an UNKNOWN result from our verification engines does not mean that a failure was found neither that the verification is successful: it indicates that the verification engine led to an \textit{out of memory} or a \textit{time out} situation.

@@

Related to ESBMC, we have tried two possibilities: one with Boolector and another one with Z3. The incremental option, which uses less memory, can be performed with Z3 only since ESBMC does not support the incremental mode with Boolector yet. Using ESBMC with Boolector led to an out of memory situation in all the case studies. This result was obtained in less than six minutes of execution, i.e., the 64 GB of RAM were consumed by the verification engine and the processes were killed, thus leading to an UNKNOWN result returned by ESBMC as shown in the first column of Table~\ref{cases}. However, running the same version of ESBMC but using incremental solving with Z3, the experimentation returned SAT or UNSAT to all the case studies. Related to the cases that use a 700 W PV system, ESBMC could not reach an error in all the four houses and the execution time took from 04 m 27 s to 05 m 08 s. However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system, therefore the equipment chosen is not suitable to meet the design requirements.
This verification took less than 1 s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, which is in line 3 of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code.

Concerning the CBMC tool, similar results were obtained, but with some slower time. The experimentation returned SAT or UNSAT to all the case studies. Related to the 700 W PV systems, the tool could not reach an error in all the four houses and the execution time took from 18 m 36 s to 19 m 02 s. However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code; with the same counterexample presented by ESBMC. This verification took less than 1 s to be performed as well.

@@

@@

The same five case studies were evaluated by HOMER Pro (RQ2). The simulation results showed that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance related issues. The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system (RQ2). All the simulations took less than 5 seconds (each) to be performed by HOMER Pro. %Fig. \ref{fig:homerscreen} shows one of the screens presented by HOMER Pro software, specifically to house 1.
%
%\begin{figure}[h]
%\includegraphics[width=0.8\textwidth]{homer.png}
%\centering
%\caption{HOMER simulation screen.}
%\label{fig:homerscreen}
%\end{figure}
%

%At the terminal, the command used to perform the verification is:
%\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
%
%Where:
%
%\begin{itemize}
%\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
%but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
%\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
%\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving. There are other options, but this parameter is necessary because the complexity of the algorithms. The incremental SMT solving uses few RAM memory, compared with other SMT solving. 
%During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory. The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
%\item And the last parameter says to the tool that the Z3 SMT solver will be used.
%\end{itemize}
%
%\subsection{Experimental results}
%\label{sec:results}
%---------------------------------------------------
\section{Threats to Validity}
%---------------------------------------------------
We have reported a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
Nevertheless, we have also identified three threats to the validity of our results that can further be assessed.

>>>>

This Chapter is devoted to the results of using automated verification to validate the intended behavior of stand-alone solar PV systems. Moreover, there is the comparative with a specialized simulation tool, and even the use of different verifiers who perform the automated verification in order to evaluate performance. Tables, commented reports, and graphical outputs are presented to aid the understanding.

@@

\begin{table}
\caption{Case studies: stand-alone solar PV systems.}\label{tab2}
\begin{scriptsize}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\hline
Item & House 1 & House 2 & House 3 & House 4 & House 5\\
\hline
\hline
PV Panels &  \multicolumn{4}{|c|}{3$\times$325 W: (3S)} & 4$\times$325 W: (2S-2P) \\
\hline
Batteries & \multicolumn{4}{|c|}{\makecell{4$\times$220 Ah: (2S-2P)\\ autonomy: 48 h}} & \makecell{4$\times$120 Ah: (4S)\\ autonomy: 6 h}\\
\hline
Charge Controller & \multicolumn{5}{|c|}{With MPPT of 150 V/35 A}\\
\hline
Inverter & \multicolumn{4}{|c|}{700 W, surge: 1,600 W} & 1,200 W, surge: 1,600 W\\
\hline
Power peak (W)& 342  & 253  & 263 & 322 & 814 \\
\hline
Power surge (W)& 342 & 722 & 732 & 896 & 980\\
\hline
Load curve (W) & \multicolumn{5}{|l|}{\makecell{House 1: 118-118-118-46-46-46-95-95-170-170-296-242-242-95-95-95-95-95-342-288-288-288-288-118\\House 2: 136-136-136-136-136-136-67-67-184-184-184-184-184-67-67-67-67-67-253-253-253-253-253-136\\House 3: 113-113-113-113-113-113-67-67-217-97-97-97-97-97-97-97-97-97-263-113-113-113-113-113\\House 4: 207-207-207-135-135-135-66-66-161-161-233-253-248-66-66-66-66-66-302-317-322-302-302-207\\House 5: 45-16-16-16-16-16-0-0-0-72-72-222-150-150-0-0-72-72-814-814-814-742-742-16}}\\
\hline
\makecell{Consumption\\ (kWh/day)}& 3.9 & 3.6 & 2.5 & 4.3 & 4.88\\
\hline
GPS Coordinates & \multicolumn{4}{|c|}{\makecell{2$^{o}$44'50.0"S 60$^{o}$25'47.8"W\\}} & \makecell{3$^{o}$4'20.208"S \\60$^{o}$0'30.168"W}\\
\hline
Details & \multicolumn{4}{|c|}{\makecell{Riverside indigenous community\\Rural Area of Manaus - Brazil}} & \makecell{Urban house \\Manaus-Amazonas-Brazil}\\
\hline
\hline
\end{tabular}
Legend: (S): Series; (P): Parallel.
\end{scriptsize}
\end{table}

@@

%\section{Verifiers Environment}
%\label{sec:verifenviron}

%------------------------------------------
\section{Results and Discussion}
\label{sec:results_indeed}
%------------------------------------------

This Section presents the results, with commented outputs produced by every tool, mainly related to the reports (CBMC and ESBMC) and some graphical resources (CPAchecker and ESBMC).

%\textcolor{red}{We should answer the two% research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
%\begin{enumerate}
%\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
%\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
%
Table~\ref{cases} summarizes the results. The times reported in Table~\ref{cases} answer RQ2. 
Note that an UNKNOWN result from our verification engines does not mean that a failure was found neither that the verification is successful: it indicates that the verification engine led to an \textit{out of memory} or a \textit{time out} situation.

@@

\subsection{ESBMC}
Related to ESBMC, we have tried two possibilities: one with Boolector and another one with Z3. The incremental option, which uses less memory, can be performed with Z3 only since ESBMC does not support the incremental mode with Boolector yet.

Using ESBMC with Boolector led to an out of memory situation in all the case studies. This result was obtained in less than six minutes of execution, i.e., the 64 GB of RAM were consumed by the verification engine and the processes were killed, thus leading to an UNKNOWN result returned by ESBMC as shown in the first column of Table~\ref{cases}.

However, running the same version of ESBMC but using incremental solving with Z3, the experimentation returned SAT or UNSAT to all the case studies.

Related to the cases that use a 700 W PV system (house 1, house 2, house 3, and house 4), ESBMC could not reach an error in all the four houses and the execution time took from 04 m 27 s to 05 m 08 s. Fig.~\ref{fig:esbmcverifhouse1} shows the output report of the tool, with the absence of fail at the end of analysis.

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{esbmcverifh1.png}
\centering
\caption{Report generated by ESBMC (with Z3 solver) after validation of House 1.}
\label{fig:esbmcverifhouse1}
\end{figure}

However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code, thereby indicating that the system is \textit{incorrectly} sized; in particular, the counterexample provided by the verification engine indicated that the nominal current from the charge controller is less than the minimum current demanded by the PV system, therefore the equipment chosen is not suitable to meet the design requirements. Fig.~\ref{fig:esbmcverifhouse5} shows the report issued by the tool, with red highlights for the result, showing the incompatibility of the sized charge controller and the minimum necessary. This verification took less than 1 s to be performed, as indicated in the last line of Table~\ref{cases}, and it is faster than the previous analysis because ESBMC stops during the sizing check, which is in line 3 of Algorithm~\ref{alg:verification-algorithm}, and does not perform the rest of verification code.

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{esbmcverifh5.png}
\centering
\caption{Report generated by ESBMC (with Z3 solver) after validation of House 5.}
\label{fig:esbmcverifhouse5}
\end{figure}

%At the terminal, the command used to perform the verification is:
%\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
%
%Where:
%
%\begin{itemize}
%\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
%but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
%\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
%\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving. There are other options, but this parameter is necessary because the complexity of the algorithms. The incremental SMT solving uses few RAM memory, compared with other SMT solving. 
%During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory. The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
%\item And the last parameter says to the tool that the Z3 SMT solver will be used.
%\end{itemize}
%

\subsection{CBMC}

Concerning the CBMC tool, similar results were obtained, but with some slower time than ESBMC. The experimentation returned SAT or UNSAT to all the case studies. Related to the 700 W PV systems (house 1, house 2, house 3, and house 4), the tool could not reach an error in all the four houses and the execution time took from 18 m 36 s to 19 m 02 s.

Fig. \ref{fig:cbmcverifhouse1} shows part of report produced by CBMC when validating the house 1. The file produced by CBMC is 160 lines long and 12.4 kB of size. The author highlighted the result, which shows that was not found design flaws within the bound $k$ of 100.

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{cbmcverifh1.png}
\centering
\caption{Report generated by CBMC after validation of House 1.}
\label{fig:cbmcverifhouse1}
\end{figure}

However the 1,200 W PV system (house 5) failed (SAT) in line 337 of the code; with the same counterexample presented by ESBMC. This verification took less than 1 s to be performed as well. Fig.~\ref{fig:cbmcverifhouse5} shows the (edited) report produced, with the highlights about the flaw found: the minimum controller current needed to the PV systems is not compatible with the chosen controller of the sized system.

\begin{figure}[h]
\includegraphics[width=0.7\textwidth]{cbmcverifh5.png}
\centering
\caption{Report generated by CBMC after validation of House 5.}
\label{fig:cbmcverifhouse5}
\end{figure}

\subsection{CPAchecker}

@@

\subsection{HOMER Pro Environment}
\label{sec:homerenviron}

Screens and comments about the simulation tool.
The same five case studies were evaluated by HOMER Pro (RQ2). The simulation results showed that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance related issues. The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system (RQ2). All the simulations took less than 5 seconds (each) to be performed by HOMER Pro. %Fig. \ref{fig:homerscreen} shows one of the screens presented by HOMER Pro software, specifically to house 1.
%
%\begin{figure}[h]
%\includegraphics[width=0.8\textwidth]{homer.png}
%\centering
%\caption{HOMER simulation screen.}
%\label{fig:homerscreen}
%\end{figure}
%

\subsection{Comparing Automated Verification and Simulation Results with Real PV Systems}

@@

%\subsection{Experimental results}
%\label{sec:results}
%---------------------------------------------------
\section{Threats to Validity}
%---------------------------------------------------
We have reported a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
Nevertheless, we have also identified three threats to the validity of our results that can further be assessed.
